---
title: "SentimentAnalysis_Magallanes-Trongoy-Nava"
author: "Killy Magallanes"
date: "2024-12-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries


```{r}
library(tidyverse)
library(lubridate)
library(tidytext)
library(ggplot2)
library(scales)
```


Load Data
```{r}
# Load the dataset
tweets_df <- read.csv("TweetsDF.csv", stringsAsFactors = FALSE)

# Display the first few rows of the dataset
head(tweets_df)
```
Data Cleaning
```{r}
# Remove duplicates
tweets_df <- tweets_df %>% distinct()

# Convert created column to date-time
tweets_df$created <- as.POSIXct(tweets_df$created, format="%Y-%m-%d %H:%M:%S")

# Remove rows with missing text
tweets_df <- tweets_df %>% filter(!is.na(text))

# Display the cleaned dataset
glimpse(tweets_df)
```

Sentiment Analysis
```{r}
# Unnest tokens and perform sentiment analysis
sentiment_df <- tweets_df %>%
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("bing")) %>%
  count(screenName, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment_score = positive - negative)

# Display sentiment scores
head(sentiment_df)
```
Trend analysis

```{r}
# Create a new column for date
tweets_df$date <- as.Date(tweets_df$created)

# Count tweets per day
daily_tweets <- tweets_df %>%
  group_by(date) %>%
  summarise(tweet_count = n())

# Plot the trend of tweets over time
ggplot(daily_tweets, aes(x = date, y = tweet_count)) +
  geom_line(color = "blue") +
  labs(title = "Trend of Tweets Over Time",
       x = "Date",
       y = "Number of Tweets") +
  theme_minimal()
```
Sentiment Score Validation

```{r}
# Plot sentiment scores
ggplot(sentiment_df, aes(x = screenName, y = sentiment_score, fill = sentiment_score > 0)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Sentiment Scores by User",
       x = "User ",
       y = "Sentiment Score") +
  scale_fill_manual(values = c("red", "green"), labels = c("Negative", "Positive")) +
  theme_minimal()
```
The sentiment score visualization shows the sentiment of tweets by user. Positive scores indicate a higher number of positive words in their tweets, while negative scores indicate the opposite. This can help identify which users are more positive or negative about a topic.

In this analysis, we performed sentiment analysis and trend analysis on a dataset of tweets. We cleaned the data, analyzed the sentiment of the tweets, and visualized trends over time. The insights gained can be useful for understanding public sentiment and engagement on social media platforms.
